Distinguishing multiple-merger from Kingman coalescence using two-site frequency spectra

### 2018-10-08 manuscript/manuscript.tex
Update acknowledgements.

\subsection*{Acknowledgements}
DPR was supported by the Chicago Fellows Program of the University of Chicago.
[OTHER FUNDING].
We thank
Arjun Biddanda,
Maryn Carlson,
Ivana Cvijovi\'c,
Ben Good,
Dick Hudson,
Evan Koch,
Joe Marcus,
Richard Neher,
Matthias Steinr\"ucken,
and Aleksandra Walczak for helpful discussions and comments on the manuscript.

>>>>

\subsection*{Acknowledgements}
DPR was supported by the Chicago Fellows Program of the University of Chicago.
[OTHER FUNDING].
This work was completed in part with resources provided by the University of Chicago Research Computing Center and Harvard Faculty of Arts and Sciences Research Computing Center.
We thank
Arjun Biddanda,
Maryn Carlson,
Ivana Cvijovi\'c,
Ben Good,
Dick Hudson,
Evan Koch,
Joe Marcus,
Richard Neher,
Matthias Steinr\"ucken,
John Wakeley,
and Aleksandra Walczak for helpful discussions and comments on the manuscript.

\subsection*{Competing interests}
The authors have no competing interests.
